Stochastic blockmodeling of relational event dynamics

### 2012-06-01 docs/discussion.tex
Incorporate Padhraic's change in the end of the discussion.

Other theories could be explored by including relevant statistics in the specification of $\mathbf{s}(t,i,j,\mathcal{A}_t)$, and similarly one can use our method to study how the roles of these statistics vary across nodes.  
One interesting extension, analogous to \cite{Airoldi2008}, would allow the latent class $z_i$ to be drawn from node-specific membership vectors $\pi_i$  after each change point.  
We leave this to future work.
%Alternatively, if nodes change groups.
%In some contexts such extensions might be substantively important and warrant future work.

>>>>

Another direction to explore is that of including different statistics in the specification of $\mathbf{s}(t,i,j,\mathcal{A}_t)$, and using our approach to study how the roles of these statistics vary across nodes.  
One potentially interesting extension, analogous to \cite{Airoldi2008}, would be to allow the latent class $z_i$ to be drawn from node-specific membership vectors $\pi_i$  after each change point---we leave this to future work.

%Other theories could be explored by including relevant statistics in the specification of $\mathbf{s}(t,i,j,\mathcal{A}_t)$, and similarly one can use our method to study how the roles of these statistics vary across nodes.  
%One interesting extension, analogous to \cite{Airoldi2008}, would allow the latent class $z_i$ to be drawn from node-specific membership vectors $\pi_i$  after each change point.  We leave this to future work.
%Alternatively, if nodes change groups.
%In some contexts such extensions might be substantively important and warrant future work.
